Reproducible Research in R: A tutorial on how to do the same thing more than once

### 2021-10-07 manuscript.Rmd
cite r packages for simulating data closes #258

The workflow described in this paper facilitates a rigorous solution to this problem:
Instead of describing the analysis in prose, researchers include the code required to conduct the analysis in the preregistration.
We term this approach of writing and publishing code at the preregistration stage *preregistration as code (PAC)*.
PAC has the potential to eliminate researchers degrees of freedom to a much greater extent than, e.g., preregistration templates.
Moreover, it removes the necessity to write two separate documents:
A preregistration *and* a manuscript.
For a PAC, researchers can write a reproducible, dynamically generated draft of their intended manuscript at the preregistration stage.
This already includes most typical sections, such as Introduction, Methods, and Results.
These results are initially based on simulated data with the same structure as the data they expect to obtain from their experiments.
For guidance on how to simulate data, see @morrisUsingSimulationStudies2019, @paxtonMonteCarloExperiments2001 and @skrondalDesignAnalysisMonte2000.
Once the preregistration is submitted and real data have been collected or made available,
the document can be reproduced with a single command, thus updating the Results section to the final version.
Reproducibility is of utmost importance at this stage since the preregistration must produce valid results at two points in time, once before data collection and once after data collection.
As outlined before, reproducibility builds upon four pillars (Version control, Dynamic document generation, Dependency tracking, Software management)
We can therefore only recommend PAC when the dangers to reproducibility we described above are eliminated.

>>>>

The workflow described in this paper facilitates a rigorous solution to this problem:
Instead of describing the analysis in prose, researchers include the code required to conduct the analysis in the preregistration.
We term this approach of writing and publishing code at the preregistration stage *preregistration as code (PAC)*.
PAC has the potential to eliminate researchers degrees of freedom to a much greater extent than, e.g., preregistration templates.
Moreover, it removes the necessity to write two separate documents:
A preregistration *and* a manuscript.
For a PAC, researchers can write a reproducible, dynamically generated draft of their intended manuscript at the preregistration stage.
This already includes most typical sections, such as Introduction, Methods, and Results.
These results are initially based on simulated data with the same structure as the data they expect to obtain from their experiments.
For guidance on how to simulate data, see @morrisUsingSimulationStudies2019, @paxtonMonteCarloExperiments2001 and @skrondalDesignAnalysisMonte2000 as well as the R packages [`simstudy`](https://cran.r-project.org/web/packages/simstudy/vignettes/simstudy.html)[@simstudy] and [`psych`](https://personality-project.org/r/psych/help/sim.html)[@psych].

Once the preregistration is submitted and real data have been collected or made available,
the document can be reproduced with a single command, thus updating the Results section to the final version.
Reproducibility is of utmost importance at this stage since the preregistration must produce valid results at two points in time, once before data collection and once after data collection.
As outlined before, reproducibility builds upon four pillars (Version control, Dynamic document generation, Dependency tracking, Software management)
We can therefore only recommend PAC when the dangers to reproducibility we described above are eliminated.
